Satisfiability Modulo Theories Competition (SMT-COMP) 2012: Rules and Procedures \\ \small{Draft for comment \\ (comments due to organizers by 31 January 2012)}

### 2012-01-27 rules/rules12.tex
Updates to web pages for announcements

\title{DRAFT DRAFT Satisfiability Modulo Theories Competition (SMT-COMP) 2012: Rules and 
Procedures
}

@@

\author{
Roberto Bruttomesso\\
Computer Science\\
USI, Lugano (Switzerland)
\and
David R. Cok \\
GrammaTech, Inc. \\
Ithaca, NY USA \\
\and
Alberto Griggio\\
ES Division\\
FBK, Trento (Italy)
}

@@

@@

The rest of this document, updated from the last year's
version\footnote{Earlier versions of this document include contributions from
Clark Barrett, Albert Oliveras, Aaron Stump, and Morgan Deters.},
describes the rules and competition procedures for SMT-COMP~2012.
The principal changes from last year's version are the following:

\item We are concentrating on just a few of the benchmark divisions this year.
  Some divisions, such as QF\_UF, are subsumed into more expressive
  logics; others have received only light interest in past competitions. Our goal is to
  focus the competition on divisions of particular interest to
  applications. To encourage new entrants, we will also accept
  solvers against any benchmark class in an exhibition category:
  results will be displayed and publicly reported.

\item We are retaining and accenting last year's ``application track" and
  encourage submission of benchmarks and competition against these
  benchmarks.

@@

\item We are adding an ``unsat core" division of QF\_BV.

\item We will have an exhibition division of solvers that produce proofs.

@@

Additionally, non-competitive divisions and tracks will not be exhibited as
part of the competition: at least two competitors must be entered
into a division for it to run as part of the competition.
If necessary, and based on final submissions, the organizers may elect to
combine competition divisions to make them competitive (such decisions will
be made with input from the community).

@@

For participation in SMT-COMP, a solver must be
uploaded as a ``competition'' solver via the StarExec upload
mechanism, or, alternatively, a previously-uploaded solver may be
marked as a ``competition'' solver.  In either case, \emph{uploads
must be marked for competition before the deadline;} uploading a solver
to StarExec is not sufficient for competition entry if it's not marked
as being a competition entrant.  The md5 checksums of competition
submissions will be public immediately after the deadline for competition
entry has passed to ensure transparency, and the submissions themselves
will be made public after the competition.  Source code need not be
provided.  However, in order to encourage sharing of source code, extra
recognition will be given to solvers providing source code distributions
including recognition for the top such solver in each division.  Instructions
for uploading solvers and machine specifications will be posted as soon
as they are available.

@@

The versions that are present on StarExec at the conclusion of the
grace period will be the ones used for the competition, and versions
submitted after this time will not be used.  The organizers reserve
the right to start the competition itself at any time after the open
of the New York Stock Exchange on the morning of June~22.  See
Section~\ref{sec:timeline} below for a full timeline.

@@

Solvers will be publicly evaluated in the following tracks, listed here and 
described in detail below. In exhibition tracks, solvers are evaluated and results posted, but no awards are announced. The other tracks are competition tracks; if there are sufficient entrants, a winner will be announced.
\begin{itemize}
\item a main track: sequential execution evaluated separately on benchmarks from each of several different logics
\item a parallel track: parallel execution evaluated on the same benchmarks and the same divisions as the main track
\item application track: evaluation on command scripts [TODO: FOR WHICH LOGICS]
\item exhibition track: solvers (particularly new entrants) may be submitted against any benchmark division; the solver will be evaluated and the results posted, though not included in competition
\item unsat-core track: a competition among solvers capable of computing unsat cores
\item proof-generation exhibition: an exhibition track for solvers capable of generating proofs
\end{itemize}

@@

If there are enough competitors to run the parallel track, we intend
to run it before or after the main competition (depending on the
estimated duration of the track).

@@

\begin{enumerate}
\item The (single) $\akey{set-logic}$ command setting the benchmark's
logic is the first command.
% rb 25/3: added
% \item A (single) \akey{set-option :print-success false} command, sent just
%       after $\akey{set-logic}$. This is to
%       avoid the output ``\texttt{success}'' to interfere with the
%       answer of the solver to the benchmark. 
\item The $\akey{exit}$ command is the last command.
\item There is exactly one $\akey{check-sat}$ command,
following possibly several $\akey{assert}$ commands.
\item There is at most one $\akey{set-info}$ command for \texttt{status}.
%%%%%%%%%%%%%%%%%%% TODO: Need to define the set-info command.
\item The formulas in the script belong to the benchmark's logic, with
any free symbols declared in the script.
\item Extra symbols are declared exactly once before any
  use, using $\akey{declare-sort}$
  %, $\akey{define-sort}$,
  %$\akey{declare-fun}$, or $\akey{define-fun}$.  
  or $\akey{declare-fun}$.
  They must be part of the allowed signature expansion for the logic.
  Moreover, all sorts declared with a $\akey{declare-sort}$ command must have zero arity.
\item In the unsat-core competition, the $\akey{set-logic}$ command is preceded by a 
$\akey{set-option :produce-unsat-cores true}$ command and the 
$\akey{check-sat}$ command is followed by a $\akey{get-unsat-core}$ command.
Also, some or all of the $\akey{assert}$ commands will assert named formula
(for example, \akey{assert (! P :named F1)}). The $\akey{get-unsat-core}$
command must return a parenthesized list of formula names, as specified by the 
SMTLIBv2 standard.
\item In the proof generation competition, the $\akey{set-logic}$ command is preceded by a 
$\akey{set-option :produce-proofs true}$ command and the 
$\akey{check-sat}$ command is followed by a $\akey{get-proof}$ command.
The $\akey{get-proof}$ command must return a proof in a solver-dependent format as an
S-expression.
\item No other commands besides the ones just mentioned may be used.

@@

\header{Timeouts.} %
Each SMT-COMP solver will be executed on an
unloaded competition machine for each given formula, up to a fixed
time limit.  The time limit is yet to be determined, but it is
anticipated to be 20 minutes, as it was in 2011.  Solvers that take more than this
time limit will be killed.  Solvers are allowed to spawn other
processes.  These will be killed at approximately the same time as the
first started process, using the TreeLimitedRun script, developed for
the CASC competition and available on the SMT-COMP web page.  A
timeout scores the same as if the output is ``\texttt{unknown}''.
%%%%%%%%%%% TODO: Clarify time limit

\header{Aborts and unparsable output.} %
Solvers which exit before the time
limit without reporting a result (\ie\ due to exhausting memory, crashing,
or producing output other than \texttt{sat}, \texttt{unsat}, or
\texttt{unknown})
will be considered to have aborted. 
An abort scores the same as if the output is ``\texttt{unknown}''. 
% rb 25/3: added
Also, as a further measure to prevent misjudgments of solvers,
any  ``\texttt{success}'' outputs will be 
ignored\footnote{
Note that SMT-LIBv2 requires to produce a ``\texttt{success}'' answer
after each \akey{set-logic}, \akey{declare-sort}, \akey{declare-fun} and
\akey{assert} command (among others), unless the option
\akey{:print-success} is set to false; ignoring the
\texttt{success} outputs therefore allows for submitting fully-compliant
solvers without the need of a wrapper script, while still allowing entrants
of previous competitions to run without changes.}.

@@

\header{Input and Output.}
Participating solvers will be connected to a trace executor 
which will incrementally send commands to the standard input channel of the solver
and read responses from the standard output channel of the solver.
The commands will be taken from an \textbf{incremental benchmark script},
which is an SMT-LIB 2.0 script which satisfies points 1., 2., 4.--7. of the definition of benchmark script given in \S\ref{sec:exec:main}, plus the following:

\begin{enumerate}
\item[3'.] There are one or more \akey{check-sat} commands, 
  each preceded by one or more \akey{assert} commands 
  and zero or more \akey{push 1} commands, 
  and followed by zero or more \akey{pop 1} commands.
\end{enumerate}

\noindent
Furthermore, the trace executor will send a single 
\akey{set-option :print-success true} command to the solver before 
sending commands from the incremental benchmark script.

\medskip
Solvers must respond immediately to the commands sent by the trace executor, 
with the answers defined in the SMT-LIB 2.0 format specification, that is,
with a \texttt{success} answer for 
\akey{set-option}, 
\akey{declare-sort}, 
\akey{declare-fun}, 
\akey{assert}, 
\akey{push 1}, 
and \akey{pop 1} 
commands,
and with a \texttt{sat}, \texttt{unsat}, or \texttt{unknown} 
for \akey{check-sat} commands.

\header{Timeouts.}
A time limit is set for the whole execution of each application
benchmark (consisting of multiple queries).  We anticipate the
timeout to be around 30~minutes (as it was in 2011).

\subsection{Exhibition track}

To encourage new entrants in any logic, we will have an exhibition track.
Any solver submitted for ``competition'' in a non-competitive track will
be executed on benchmarks for the logic divisions chosen for that solver.
The results will be made public and the solver acknowledged. Any logic divisions
for which there are benchmarks may be specified.

@@

Similarly, the competition will feature an exhibition track of proof-generating solvers. This is
simply an exhibition track because there is as yet no SMT-LIB standard way to express proofs. We hope
that encouraging the capability in solvers will also encourage a common proof format. The exhibition
will count the number of benchmarks for which a solver successfully generates a proof; the proofs 
themselves may be spot checked by hand or in a semi-automated fashion, depending on the format.

TODO: What benchmark logics will be used.

@@

We expect the problem divisions for SMT-COMP 2012 to include the following
SMT-LIB \emph{logics}.  These logics are specified in SMT-LIB format on the
SMT-LIB web page.  Note that the ``QF\_'' prefix means the division's
formulas are quantifier-free.  However, the organizers reserve the right to add
(remove) divisions if (not) enough benchmarks and solvers exist for a
particular division.

@@

@@

When 5 or more solvers are used for the
calculation, two times are dropped from the calculation of the average
(one at the maximum and one at the minimum).  Solvers giving an
incorrect answer are not counted in the average; solvers crashing,
timing out, or giving an unknown result are considered as taking 30
minutes (which, with the above formula, pulls the difficulty
toward~5.0).  If there are available solvers, but no average is
defined under these rules, the difficulty shall be 5.0.  For new
divisions, where there are no available solvers to compute the
difficulty, the difficulty will be computed using whatever means are
available to the organizers for that purpose.

@@

@@

Pseudo-random numbers will be generated using the standard C library
function \texttt{random()}, seeded (using \texttt{srandom()}) with the
sum, modulo $2^{30}$, of the numbers provided in the system
descriptions (see Section~\ref{sec:entrants} above) by all SMT-COMP
entrants other than the organizers.  Additionally, the integer part of
the opening value of the New York Stock Exchange Composite Index on
June~25
will be added to the other seeding values.  This helps provide transparency,
by guaranteeing that the organizers cannot manipulate the seed in
favor of or against any particular submitted solver.  Benchmarks will also be slightly
scrambled before the competition, using a simple benchmark scrambler
seeded with the same seed as the benchmark selector.  Both the
scrambler and benchmark selector will be publicly available before the
competition.  Naturally, solvers must not rely on previously
determined identifying syntactic characteristics of competition
benchmarks in testing satisfiability (violation of this is considered
cheating).

@@

\header{Benchmark demographics and selection.} 
All the available benchmarks will be used for the competition. 
As was the case in 2011, no difficulty will be assigned to the benchmarks for the application track.
Benchmarks will be slightly scrambled before the competition, using the same scrambler and 
random seed as the main track. 
% rb 25/3: added
For this year, the selection algorithm for the application track will be chosen after the
 April 15th deadline, when the exact demographic of the benchmarks (collected with a usual
``call for benchmarks'') will be available.

TODO: Divisions for unsat core and proof tracks

@@

\header{Main and application tracks}
The score for each benchmark is a triple $\langle e,n,m\rangle$, with
$e$ a non-negative number of erroneous results,
$n\in[0,N]$ an integral number of points scored for the benchmark,
where $N$ is the number of \akey{check-sat} commands
in the benchmark, and $m\in[0,T]$ is the (real-valued) time is seconds, where $T$ is
the timeout.  Recall that main track benchmarks will have just one \akey{check-sat} command;
application track benchmarks may have multiple \akey{check-sat} commands.
The score for the benchmark is initialized with
$\langle0,0,0\rangle$ and then computed as follows.
\begin{itemize}
\item A correctly-reported \texttt{sat} or \texttt{unsat} answer after
  $s$~seconds (counting from the beginning of this particular
  \akey{check-sat}) contributes $\langle0,1,s\rangle$ to the running
  score.
\item An answer of \texttt{unknown}, an unexpected answer, a crash, or a memory-out during
  execution of the query, or a benchmark timeout, aborts the execution
  of the benchmark and assigns the current value of the running score
  to the benchmark.  (Recall that there is one timeout for the entire
  benchmark; there are no individual timeouts for queries.)
\item An incorrect answer to a \akey{check-sat} command has the effect of terminating the
  evaluation of that individual benchmark, and the returned score for the benchmark
  will be $\langle1,0,0\rangle$.
\end{itemize}

@@

\header{Number of competitors}
Winners in each Problem Division for which there are at least three
entrants from distinct research groups competing will be taken to be
those with the highest score and no erroneous results. In addition to recognizing the overall
winner in each division, the top solver that provides its source code will also be
recognized in each division.  
For Problem Divisions with fewer than three
entrants, the results will be reported but no winner officially
declared.

@@

\nobreak
\vbox{% no page break here, please!
\begin{description}
\item[March 15] First version of the benchmark library for the application track posted for comment.
  First version of the benchmark scrambler, benchmark selector and trace exector made available.
\item[April 15] Final version of the benchmark scrambler, benchmark selector and trace exector made available.
\item[April 15] No new benchmarks can be added after this date, but
  problems with existing benchmarks may be fixed.
\item[June 1] Benchmark libraries are frozen.
\item[June 15 (7pm EDT)] Solvers due via StarExec (for
  all tracks), including system
  descriptions and magic numbers for benchmark scrambling.
\item[June 18 (7pm EDT)] Final versions due, fixing any last-minute
 bugs (this marks the end of the grace period for
 submissions).
\item[June 22] Opening value of NYSE Composite Index used to complete random seed.
\item[June 25--29] Anticipated dates for SMT-COMP 2012.
\end{description}}

@@

\item Alberto Griggio and Roberto Bruttomesso are co-organizers. They 
were also co-organizers in 2011. They are responsible for bringing 
recommendations from the previous year's experience. They will also 
be validating the competition setup, checking benchmarks, and
operating the competition. They are associated with solver groups
that will be submitting the solvers 
MathSat and OpenSMT, respectively.
\end{itemize}
\bibliographystyle{plain}
\bibliography{biblio}

>>>>

\title{Satisfiability Modulo Theories Competition (SMT-COMP) 2012: Rules and 
Procedures \\
\small{Draft for comment \\
(comments due to organizers by 31 January 2012)}
}

@@

\author{
Roberto Bruttomesso\\
Dept. of Computer Science\\
University of Milan, Milan (Italy)
\and
David R. Cok \\
GrammaTech, Inc. \\
Ithaca, NY (USA) \\
\and
Alberto Griggio\\
ES Division\\
FBK, Trento (Italy)
}

@@

\noindent This is a preliminary version of the 2012 SMT-COMP rules, issued for comment
by potential participants. Comments should be emailed to the smtcomp mailing
list or, if necessary, directly to the organizers. To receive full consideration,
comments must be received by 31 January 2012.

@@

Accordingly, researchers are highly encouraged to submit both new benchmarks
and new or improved solvers to raise the level of competition and advance
the state-of-the-art in automated SMT problem solving.

Note that SMTCOMP 2012 has several tracks: a main track, a parallel track, an
application track, an unsat-core track, and a proof-generation track.
Within a track there are one or more divisions, where each division
uses benchmarks from a specific SMT-LIB logic (or group of logics).

The rest of this document, updated from the last year's
version\footnote{Earlier versions of this document include contributions from
Clark Barrett, Albert Oliveras, Aaron Stump, and Morgan Deters.},
describes the rules and competition procedures for SMT-COMP~2012.
The principal changes from last year's version are the following:
\begin{itemize}

\item In the main and parallel competition, we are concentrating on just a few of the benchmark divisions this year.
  Some divisions, such as QF\_UF, are subsumed into more expressive
  logics; others have received only light interest in past competitions. Our goal is to
  focus the competition on divisions of particular interest to
  applications. Solvers requesting to be run against other benchmark divisions are
  welcome and will be run in exhibition mode:
  results will be displayed and publicly reported.

\item We are retaining and accenting last year's ``application track" and
  encourage submission of benchmarks for this track and competition against these
  benchmarks.

@@

\item We are adding an ``unsat core" track.

\item We will have an exhibition track of solvers that produce proofs.

@@

Additionally, non-competitive divisions will not be exhibited as
part of the competition: at least two competitors must be entered
into a division for it to run as part of the competition.
If necessary, and based on final submissions, the organizers may elect to
combine competition divisions to make them competitive (such decisions will
be made with input from the community).

@@

For participation in SMT-COMP, a solver must be
uploaded as a ``competition'' solver via the StarExec upload
mechanism, or, alternatively, a previously-uploaded solver may be
marked as a ``competition'' solver.  In either case, \emph{uploads
must be marked for competition before the deadline;} uploading a solver
to StarExec is not sufficient for competition entry if it is not marked
as being a competition entrant.  The md5 checksums of competition
submissions will be public immediately after the deadline for competition
entry has passed to ensure transparency, and the submissions themselves
will be made public after the competition.  Source code need not be
provided.  However, in order to encourage sharing of source code, extra
recognition will be given to solvers providing source code distributions
including recognition for the top such solver in each division.  Instructions
for uploading solvers and machine specifications will be posted as soon
as they are available.

@@

The versions that are present on StarExec at the conclusion of the
grace period will be the ones used for the competition, and versions
submitted after this time will not be used.  The organizers reserve
the right to start the competition itself at any time after the open
of the New York Stock Exchange on the morning of June~20.  See
Section~\ref{sec:timeline} below for a full timeline.

@@

Solvers will be publicly evaluated in the following tracks, listed here and 
described in detail below. In exhibition divisions of these tracks, solvers are evaluated and results posted, but no awards are announced. The other divisions are competition divisions; if there are sufficient entrants, a winner will be announced.
\begin{itemize}
\item a main track: sequential execution evaluated separately on benchmarks from each of several different logics (some competitive and some exhibition divisions)
\item a parallel track: parallel execution evaluated on the same benchmarks and the same divisions as the main track (some competitive and some exhibition divisions)
\item application track: evaluation on command scripts (all divisions with sufficient benchmarks and entrants are competitive)
\item unsat-core track: a competition among solvers capable of computing unsat cores
\item proof-generation exhibition: an exhibition track for solvers capable of generating proofs
\end{itemize}

@@

If there are enough competitors to run the parallel track, we intend
to run it before or after the main competition (depending on the
estimated duration of the track). We may choose to use an NYSE seed from a different date
to accommodate an early start.

@@

\begin{enumerate}
\item The (single) $\akey{set-logic}$ command setting the benchmark's
logic is the first command after any $\akey{set-option}$ commands described below.
% rb 25/3: added
% \item A (single) \akey{set-option :print-success false} command, sent just
%       after $\akey{set-logic}$. This is to
%       avoid the output ``\texttt{success}'' to interfere with the
%       answer of the solver to the benchmark. 
\item The $\akey{exit}$ command is the last command.
\item For tracks other than the application track, there is exactly one $\akey{check-sat}$ command,
following possibly several $\akey{assert}$ commands.
\item For the application track, there are one or more \akey{check-sat} commands, 
  each preceded by one or more \akey{assert} commands 
  and zero or more \akey{push 1} commands, 
  and followed by zero or more \akey{pop 1} commands.
\item Scripts for the application track will have an initial $\akey{set-option :print-success true}$ command.
\item There is at most one $\akey{set-info}$ command for \texttt{status}.
%%%%%%%%%%%%%%%%%%% TODO: Need to define the set-info command.
\item The formulas in the script belong to the benchmark's logic, with
any free symbols declared in the script.
\item Extra symbols are declared exactly once before any
  use, using $\akey{declare-sort}$
  %, $\akey{define-sort}$,
  %$\akey{declare-fun}$, or $\akey{define-fun}$.  
  or $\akey{declare-fun}$.
  They must be part of the allowed signature expansion for the logic.
  Moreover, all sorts declared with a $\akey{declare-sort}$ command must have zero arity.
\item In the unsat-core competition, the $\akey{set-logic}$ command is preceded by a \\
$\akey{set-option :produce-unsat-cores true}$ command and the 
$\akey{check-sat}$ command is followed by a $\akey{get-unsat-core}$ command.
Also, some or all of the $\akey{assert}$ commands will assert named formula
(for example, \akey{assert (! P :named F1)}). The $\akey{get-unsat-core}$
command must return a parenthesized list of formula names, as specified by the 
SMTLIBv2 standard.
\item In the proof generation competition, the $\akey{set-logic}$ command is preceded by a \\
$\akey{set-option :produce-proofs true}$ command and the 
$\akey{check-sat}$ command is followed by a $\akey{get-proof}$ command.
The $\akey{get-proof}$ command must return a proof in a solver-dependent format made known to the organizers.
\item No other commands besides the ones just mentioned may be used.

@@

Solvers that register in non-competition logic divisions (cf. section \ref{sec:theories})
will be run in an exhibition mode: results will be generated and publicly
posted, but no awards will be announced.

\header{Timeouts.} %
Each SMT-COMP solver will be executed on an
unloaded competition machine for each given formula, up to a fixed
time limit.  The time limit is yet to be determined, but it is
anticipated to be 20 minutes, as it was in 2011.\footnote{The time limit may be adjusted once we understand the resources and capabilities of the StarExec service.} 
Solvers that take more than this
time limit will be killed.  Solvers are allowed to spawn other
processes.  These will be killed at approximately the same time as the
first started process, using the TreeLimitedRun script, developed for
the CASC competition and available on the SMT-COMP web page.  A
timeout scores the same as if the output is ``\texttt{unknown}''.
%%%%%%%%%%% TODO: Clarify time limit

\header{Aborts and unparsable output.} %
Solvers which exit before the time
limit without reporting a result (\ie\ due to exhausting memory, crashing,
or producing output other than \texttt{sat}, \texttt{unsat}, or
\texttt{unknown})
will be considered to have aborted. 
An abort scores the same as if the output is ``\texttt{unknown}''. 
% rb 25/3: added
Also, as a further measure to prevent misjudgments of solvers,
any  ``\texttt{success}'' outputs will be 
ignored.\footnote{
Note that SMT-LIBv2 requires to produce a ``\texttt{success}'' answer
after each \akey{set-logic}, \akey{declare-sort}, \akey{declare-fun} and
\akey{assert} command (among others), unless the option
\akey{:print-success} is set to false; ignoring the
\texttt{success} outputs therefore allows for submitting fully-compliant
solvers without the need of a wrapper script, while still allowing entrants
of previous competitions to run without changes.}

@@

\header{Input and Output.}
Participating solvers will be connected to a trace executor 
which will incrementally send commands to the standard input channel of the solver
and read responses from the standard output channel of the solver.
The commands will be taken from an \textbf{incremental benchmark script},
which is an SMT-LIB 2.0 script which satisfies the rules for an application script given above.
Note also that the trace executor will send a single 
\akey{set-option :print-success true} command to the solver before 
sending commands from the incremental benchmark script.

\medskip
Solvers must respond immediately to the commands sent by the trace executor, 
with the answers defined in the SMT-LIB 2.0 format specification, that is,
with a \texttt{success} answer for 
\akey{set-option}, 
\akey{set-logic}, 
\akey{declare-sort}, 
\akey{declare-fun}, 
\akey{assert}, 
\akey{push 1}, 
and \akey{pop 1} 
commands,
 with a \texttt{sat}, \texttt{unsat}, or \texttt{unknown} 
for \akey{check-sat} commands, and with the defined responses for \akey{get-unsat-core} and \akey{get-proof} commands.

\header{Timeouts.}
A time limit is set for the whole execution of each application
benchmark (consisting of multiple queries).  We anticipate the
timeout to be around 30~minutes (as it was in 2011).\footnote{The timeout may be adjusted once we have experience with the abilities and resources of the StarExec service.}

@@

Similarly, the competition will feature an exhibition track of proof-generating solvers. This is
simply an exhibition track because there is as yet no SMT-LIB standard way to express proofs. We hope
that encouraging the capability in solvers will also encourage a common proof format. The exhibition
will count the number of benchmarks for which a solver successfully generates a proof.
Solvers submitted against this track must be accompanied by a description of the format of the 
generated proofs. The organizers are considering how and whether to check the proofs (with automated tools);
comment from teams submitting proof-generating solvers is welcome. %%TODO

The organizers are still reviewing which logic divisions will be supported for the unsat-core and proof generating tracks; 
those divisions will be announced later.
Input from teams considering submitting unsat-core or proof generating solvers is welcome.
%% TODO

@@

The competition divisions for SMT-COMP 2012 are planned to be the following
SMT-LIB \emph{logics}.  These logics are specified in SMT-LIB format on the
SMT-LIB web page.  However, the organizers reserve the right to add
(remove) divisions if (not) enough benchmarks and solvers exist for a
particular division.

@@

\item QF\_IDL: quantifier-free formulas to be
  tested for satisfiability modulo a background theory of integer
  arithmetic.  The syntax of atomic formulas is restricted to
  difference logic, i.e. x - y op c, where op is either equality or
  inequality and c is an integer constant. This division is included because it was highly popular in 2011.

@@

When 5 or more solvers are used for the
calculation, the maximum and the minimum times are dropped from the calculation of the average.  Solvers giving an
incorrect answer are not counted in the average; solvers crashing,
timing out, or giving an unknown result are considered as taking 30
minutes (which, with the above formula, pulls the difficulty
toward~5.0).  If there are available solvers, but no average is
defined under these rules, the difficulty shall be 5.0.  For new
divisions, where there are no available solvers to compute the
difficulty, the difficulty will be computed using whatever means are
available to the organizers for that purpose.

@@

Once the StarExec service is evaluated, and if the organizers decide that
the service has sufficient resources, the target number of benchmarks for 
a division may be increased above 200, with all subpopulations being enlarged
proportionately, insofar as there are sufficient benchmarks. The target number
of benchmarks will not be raised if that requires reducing the timeout limits
below the values used in 2011.

@@

Pseudo-random numbers will be generated using the standard C library
function \texttt{random()}, seeded (using \texttt{srandom()}) with the
sum, modulo $2^{30}$, of the numbers provided in the system
descriptions (see Section~\ref{sec:entrants} above) by all SMT-COMP
entrants other than the organizers.  Additionally, the integer part of
the opening value of the New York Stock Exchange Composite Index on
a publicized day
will be added to the other seeding values.  This helps provide transparency,
by guaranteeing that the organizers cannot manipulate the seed in
favor of or against any particular submitted solver.  Benchmarks will also be slightly
scrambled before the competition, using a simple benchmark scrambler
seeded with the same seed as the benchmark selector.  Both the
scrambler and benchmark selector will be publicly available before the
competition.  Naturally, solvers must not rely on previously
determined identifying syntactic characteristics of competition
benchmarks in testing satisfiability (violation of this is considered
cheating).

@@

\header{Benchmark demographics and selection.} 
All the available benchmarks will be used for the competition. 
As was the case in 2011, no difficulty will be assigned to the benchmarks for the application track.
Benchmarks will be slightly scrambled before the competition, using the same scrambler and 
random seed as the main track. 
The selection algorithm for the application track will be chosen after the
 April 15th deadline, when the exact demographic of the benchmarks (collected with a usual
``call for benchmarks'') will be available.

\subsection{Benchmarks for the unsat-core and proof-generation tracks}

These benchmarks will be selected from the pool of available and newly submitted benchmarks,
adjusted to add formula naming for the unsat-core track. The organizers are still discussing
which logic divisions to use.
%%TODO: Divisions for unsat core and proof tracks

@@

\header{Main and application tracks}
The score for each benchmark is a triple $\langle e,n,m\rangle$, with
$e$ a non-negative number of erroneous results,
$n\in[0,N]$ an integral number of points scored for the benchmark,
where $N$ is the number of \akey{check-sat} commands
in the benchmark, and $m\in[0,T]$ is the (real-valued) time in seconds, where $T$ is
the timeout.  Recall that main track benchmarks will have just one \akey{check-sat} command;
application track benchmarks may have multiple \akey{check-sat} commands.
The score for the benchmark is initialized with
$\langle0,0,0\rangle$ and then computed as follows.
\begin{itemize}
\item A correctly-reported \texttt{sat} or \texttt{unsat} answer after
  $s$~seconds (counting from the beginning of this particular
  \akey{check-sat}) contributes $\langle0,1,s\rangle$ to the running
  score.
\item An answer of \texttt{unknown}, an unexpected answer, a crash, or a memory-out during
  execution of the query, or a benchmark timeout, aborts the execution
  of the benchmark and assigns the current value of the running score
  to the benchmark.  (Recall that there is one timeout for the entire
  benchmark; there are no individual timeouts for queries.)
\item An incorrect answer to a \akey{check-sat} command has the effect of terminating the
  evaluation of that individual benchmark, and the returned score for the benchmark
  will be $\langle1,0,0\rangle$.
\end{itemize}

@@

\header{Number of competitors}
Winners in each competition Problem Division for which there are at least three
entrants from distinct research groups competing will be taken to be
those with the highest score and no erroneous results. In addition to recognizing the overall
winner in each division, the top solver that provides its source code will also be
recognized in each division.  
For Problem Divisions with fewer than three
entrants, the results will be reported but no winner officially
declared.

@@

\nobreak
\vbox{% no page break here, please!
\begin{description}
\item[March 15] First version of the benchmark library for the application track posted for comment.
  First version of the benchmark scrambler, benchmark selector and trace exector made available.
\item[April 15] Final version of the benchmark scrambler, benchmark selector and trace exector made available.
\item[April 15] No new benchmarks can be added after this date, but
  problems with existing benchmarks may be fixed.
\item[June 1] Benchmark libraries are frozen.
\item[June 15 (7pm EDT)] Solvers due via StarExec (for
  all tracks), including system
  descriptions and magic numbers for benchmark scrambling.
\item[June 18 (7pm EDT)] Final versions due, fixing any last-minute
 bugs (this marks the end of the grace period for
 submissions).
\item[June 20] Opening value of NYSE Composite Index used to complete random seed.
\item[June 25--29] Anticipated dates for SMT-COMP 2012.
\end{description}}

@@

\item Alberto Griggio and Roberto Bruttomesso are co-organizers. They 
were also co-organizers in 2011. They are responsible for bringing 
recommendations from the previous year's experience. They will also 
be validating the competition setup, checking benchmarks, and
operating the competition. They have been associated with solver groups
that have submitted solvers to the competition, and may again in 2012 (in 2011, 
MathSat and OpenSMT, respectively).
\end{itemize}
\bibliographystyle{plain}
\bibliography{biblio}
